### 2024-01-02 documentation/thesis/thesis_document.tex
more thesis

Another application example is when sensors are physically separated or
there are long distances between them. By connecting several sensors via
the proxy module, it is possible to link several instances and all
sensors available in the network are available to the control \gls{pc}.

@@

The figure \ref{mrp_proxy_multi.png} shows the modified
\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
both proxy instances do not communicate directly with the control
\gls{pc}, but \passthrough{\lstinline!remote (+pc) \#2!} is connected to
\passthrough{\lstinline!remote (+pc) \#1!}. This is then visible as a
sensor opposite the Control \gls{pc}, even if there are several proxy
instances behind it.

@@

The figure \ref{MRPlib_Proxy_Module.png} shows the separation of the
various \gls{hal} instances, which communicate with the physically
connected sensors on the \passthrough{\lstinline!remote!}-\gls{pc} and
the \passthrough{\lstinline!control!}-\gls{pc} side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started\ref{lst:mrpcli_proxy_start} on the
\passthrough{\lstinline!remote!} \gls{pc} side.

@@

\begin{itemize}
\item
  nummerieierung zuerst lokale sensoren dann weitere proxy sensoren
\item
  commando templating
\item
  einzelne sensor capabilites werden gemerged
\item
  ids werden aufsuimmiert
\item
  spätere sensor identifikation geschieht über die jeweilige sensor id,
  welche über diesen index abgefragt werden kann
\item
  grafik mit mergin algorithmus
\end{itemize}

@@

After generating simple measurements with random values in the previous
example\ref{mrpreading}, the next step is to record real sensor data.
For this purpose, the MRPHal module was developed, which can interact
with all
\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor}-compatible
sensors. In the following example\ref{lst:mrpexample_hal}, an
\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} is
connected locally to the host \gls{pc}.

\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of an measurement}, label=lst:mrpexample_hal]
from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
# SEARCH FOR CONNECTED SENSORS
## LISTS LOCAL CONNECTED OR NETWORK SENSORS
system_ports: MRPHalSerialPortInformation = MRPHalSerialPortInformation.list_sensors()
sensor = MRPHal(system_ports[0])
# OR USE SPECIFIED SENSOR DEVICE
device_path: MRPHalSerialPortInformation = MRPHalSerialPortInformation("UNFSensor1")
sensor = MRPHal(device_path)
# RAW SENSOR INTERACTION MODE
sensor.connect()
basesensor = MRPBaseSensor.MRPBaseSensor(sensor)
basesensor.query_readout()
print(basesensor.get_b()) # GET RAW MEASUREMENT
print(basesensor.get_b(1)) # GET RAW DATA FROM SENSOR WITH ID 1
# TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
reading_source: MRPReadingSource = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
\end{lstlisting}

In general, a sensor can be connected using its specific system path or
the sensor-\gls{id} via the MRPHalSerialPortInformation function.
Locally connected or network sensors can also be automatically
recognised using the \passthrough{\lstinline!list\_sensors!} function.
Once connected, these are then converted into a usable data source using
the MRPReadingSource module. This automatically recognises the type of
sensor and generated an \passthrough{\lstinline!MRPReading!} instance
with the measured values of the sensor.

@@

\begin{lstlisting}[language=Python]
from MRP import MRPSimulation, MRPPolarVisualization, MRPReading
# GENERATE SILUMATED READING USING A SIMULATED HALLSENSOR FROM magpy LIBRARY
reading: MRPReading = MRPSimulation.generate_reading(MRPMagnetTypes.MagnetType.N45_CUBIC_12x12x12,_add_random_polarisation=True)
# GENERATE A FULLSPHERE MAP READING
reading_fullsphere: MRPReading = MRPSimulation.generate_random_full_sphere_reading()
# RENDER READING TO FILE IN 3D
visu = MRPPolarVisualization(reading)
visu.plot3d(None)
visu.plot3d("simulated_reading.mag.png")
# EXPORT READING
reading.dump_to_file("simulated_reading.mag.json")
\end{lstlisting}

@@

Dieses beispiel zeigt

\begin{lstlisting}[language=Python]
from MRP import MRPAnalysis, MRPDataVisualization, MRPReading
# CREATE EMPTY READING
reading = MRPReading.MRPReading()
# CREATE A SAMPLE MEASUREMENT
for i in range(1000):
    measurement = MRPReadingEntry.MRPReadingEntry()
    # readout sensor or use dummy data and assign result
    measurement.value = (random.random() -0.5) * 2
    reading.insert_reading_instance(measurement, False)
# PLOT MEAN VISUALIZATION
MRPDataVisualization.MRPDataVisualization.plot_error([reading])
# APPLY COMPENSATION
# Here the ``calculate_mean`` function is used
reading_mean_value = MRPAnalysis.MRPAnalysis.calculate_mean(reading)
# we want to subtract the mean value from all readings
reading_mean_value = -reading_mean_value
# modify measurement values
MRPAnalysis.MRPAnalysis.apply_global_offset_inplace(reading, reading_mean_value)
\end{lstlisting}

@@

>>>>

Another application example is when sensors are physically separated or
there are long distances between them. By connecting several sensors via
the proxy module, it is possible to link several instances and all
sensors available in the network are available to the
\passthrough{\lstinline!control!} \gls{pc}.

@@

The figure \ref{mrp_proxy_multi.png} shows the modified
\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
both proxy instances do not communicate directly with the
\passthrough{\lstinline!control!} \gls{pc}, but
\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#2!} is
connected to
\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#1!}.
This is then visible as a sensor opposite the Control \gls{pc}, even if
there are several proxy instances behind it.

@@

The figure \ref{MRPlib_Proxy_Module.png} shows the separation of the
various \gls{hal} instances, which communicate with the physically
connected sensors on the \passthrough{\lstinline!remote!} \gls{pc} and
the \passthrough{\lstinline!control!} \gls{pc} side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started\ref{lst:mrpcli_proxy_start} on the
\passthrough{\lstinline!remote!} \gls{pc} side.

@@

As it is possible to connect many identical sensors to one host using
the \passthrough{\lstinline!network proxy!}, it must be possible to
address them separately. This separation is done by the
\passthrough{\lstinline!MRPProxy.proxy!} module and is therefore not
part of the core \gls{mrp} library.

Each connected sensor is addressed via the text-based \gls{cli} or the
binary interface, this is initially the same for each sensor. The only
identification feature is the sensor \gls{id}.

The \passthrough{\lstinline!network proxy!} instance pretends to be a
sensor to the \gls{mrp} host, so the multiple sensors must be combined
into one. This is done in several steps, in the
\passthrough{\lstinline!network proxy!} start procedure:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Construct the Sensor ID LookUp-Table}
\item
  \textbf{Merging the sensor capabilities}
\item
  \textbf{Dynamic extension of the available network proxy commands}
\end{enumerate}

@@

After generating simple measurements with random values in the previous
example\ref{mrpreading}, the next step is to record real sensor data.
For this purpose, the \passthrough{\lstinline!MRPHal!} module was
developed, which can interact with all
\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor}-compatible
sensors. In the following example\ref{lst:mrpexample_hal}, an
\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} is
connected locally to the host-\gls{pc}.

\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of an measurement}, label=lst:mrpexample_hal]
from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
# SEARCH FOR CONNECTED SENSORS
## LISTS LOCAL CONNECTED OR NETWORK SENSORS
system_ports = MRPHalSerialPortInformation.list_sensors()
sensor = MRPHal(system_ports[0])
# OR USE SPECIFIED SENSOR DEVICE
device_path = MRPHalSerialPortInformation("UNFSensor1")
sensor = MRPHal(device_path)
# RAW SENSOR INTERACTION MODE
sensor.connect()
basesensor = MRPBaseSensor.MRPBaseSensor(sensor)
basesensor.query_readout()
print(basesensor.get_b()) # GET RAW MEASUREMENT
print(basesensor.get_b(1)) # GET RAW DATA FROM SENSOR WITH ID 1
# TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
reading_source = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
\end{lstlisting}

In general, a sensor can be connected using its specific system path or
the sensor-\gls{id} via the
\passthrough{\lstinline!MRPHalSerialPortInformation!} function. Locally
connected or network sensors can also be automatically recognised using
the \passthrough{\lstinline!list\_sensors!} function. Once connected,
these are then converted into a usable data source using the
\passthrough{\lstinline!MRPReadingSource!} module. This automatically
recognises the type of sensor and generated an
\passthrough{\lstinline!MRPReading!} instance with the measured values
of the sensor.

@@

If no hardware sensor is available or for the generation of test data,
the \passthrough{\lstinline!MRPSimulation!} module is available. This
contains a series of functions that simulate various magnets and their
fields. The result is a complete \passthrough{\lstinline!MRPReading!}
measurement with a wide range of set meta data. The
example\ref{lst:mrpexample_simulation} illustrated the basic usage.
Different variations of the \passthrough{\lstinline!generate\_reading!}
function offers the user additional parameterisation options, such as
random polarisation direction or a defined centre-of-gravity vector. The
data is generated in the background using the
\passthrough{\lstinline!magpylib!}\cite{ortner2020magpylib} library
according to the specified parameters.

\begin{lstlisting}[language=Python, caption={MRPSimulation example illustrates the usage of several data analysis functions}, label=lst:mrpexample_simulation]
from MRP import MRPSimulation, MRPPolarVisualization, MRPReading
# GENERATE SILUMATED READING USING A SIMULATED HALLSENSOR FROM magpy LIBRARY
reading = MRPSimulation.generate_reading(MagnetType.N45_CUBIC_12x12x12,_add_random_polarisation=True)
# GENERATE A FULLSPHERE MAP READING
reading_fullsphere = MRPSimulation.generate_random_full_sphere_reading()
# RENDER READING TO FILE IN 3D
visu = MRPPolarVisualization(reading)
visu.plot3d(None)
visu.plot3d("simulated_reading.png")
# EXPORT READING
reading.dump_to_file("simulated_reading.mag.json")
\end{lstlisting}

@@

Once data can be acquired using hardware or software sensors, the next
step is to analyse this data. The \gls{mrp} library provides some simple
analysis functions for this purpose. The code example shows the basic
use of the module. The
\passthrough{\lstinline!Evaluation!}\ref{evaluation} chapter shows how
the user can implement their own algorithms and add them to the library.

\begin{lstlisting}[language=Python, caption={MRPAnalysis example code performs several data analysis steps}, label=lst:mrpexample_analysis]
from MRP import MRPAnalysis, MRPReading
# CREATE A SAMPLE MEASUREMENT WITH SIMULATED DATA
reading = MRPSimulation.generate_reading(MagnetType.N45_CUBIC_10x10x10)
# CALCULATE MEAN
print(MRPAnalysis.calculate_mean(reading))
# CALCULATE STD DEVIATION ON TEMPERATURE AXIS
print(MRPAnalysis.calculate_std_deviation(reading, _temperature_axis=True))
# CALCULATE CENTER OF GRAVITY
(x, y, z) = MRPAnalysis.calculate_center_of_gravity(reading)
# APPLY CALIBRATION READING TO REMOVE BACKGROUND NOISE
calibration_reading = MRPSimulation.generate_reading(MagnetType.N45_CUBIC_10x10x10, _ideal = True)
MRPAnalysis.apply_calibration_data_inplace(calibration_reading, reading)
\end{lstlisting}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
\caption{Example full sphere plot of an measurement using the
MRPVisualisation module
\label{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}}
\end{figure}

This final example shows the use of the MRP Visualisation module, which
provides general functions for visualising measurements. This makes it
possible to visually assess the results of a measurement. This is
particularly helpful for full-sphere measurements recorded with the
\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor. The
sub-module `MRPPolarVisualisation' is specially designed for these. The
figure\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
shows a plot of a fullsphere measurement.

It is also possible to export the data from the MRPAnalysis module
graphically as diagrams. The \passthrough{\lstinline!MRPVisualisation!}
modules are used here. The following
example\ref{lst:mrpexample_visualisation} shows the use of both modules.

\begin{lstlisting}[language=Python, caption={MRPVisualisation example which plots a fullsphere to an image file}, label=lst:mrpexample_visualisation]
from MRP import MRPPolarVisualization
# CREATE MRPPolarVisualization INSTANCE
## IT CAN BE REUSED CALLING plot2d AGAIN, AFTER LINKED READING DATA WERE MODIFIED
visu = MRPPolarVisualization.MRPPolarVisualization(reading)
# 2D PLOT INTO A WINDOW
visu.plot2d_top(None)
visu.plot2d_side(None)
# 3D PLOT TO FILE
visu.plot3d(os.path.join('./plot3d_3d.png'))

# PLOT ANALYSIS RESULTS
from MRP import MRPDataVisualization
MRPDataVisualization.MRPDataVisualization.plot_error([reading_a, reading_b, reading_c])
\end{lstlisting}
